---
title: "VE-RSPM DVMT Calculations"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Trace DVMT calcs for NVTA model

```{r start}
# Assumes launching this from a location where a completed VERSPM model exists.
# Here using the Northern Virginia Tranposrtaiton Authority (NVTA) model as the example

rs <- openModel('VERSPM_NVTA')
# rs$run() # do this only once. Afterwards, can just openModel and then initializeModel to get the previous model available

# View VMT and characteristics for a single household

rs$tables = 'Household'
rs$groups = '2019'
hh_table <- rs$extract(saveTo = F)
hh_table <- hh_table[[1]] # from list of one data frame to a data frame
```


# Look at characteristics

# Model 1: Probability of travel, metropolitan model

Inputs: 

- `Drivers` - number of drivers in the household
- `LogInc` - natural log of annual household income ($2001)
- `Hbppopdn` - density (pop/sq mi) of the census block group
- `NumVeh` - number of vehicles owned or leased by the household
- `ZeroVeh` - dummy variable identifying whether the household has no vehicles
- `Workers` - number of workers in the household
- `BusEqRevMiPC` - urbanized area per capita bus-equivalent transit revenue miles
- `UrbanDev` - whether the block group is characterized by urban mixed-use development

```{r model_1_values}


```


# Model 2: Power-transformed travel day DVMT

Metropolitan power transform: 0.24


- `Drivers` - number of drivers in the household
- `LogIncome` - natural log of annual household income ($2001)
- `Hbppopdn` - density (pop/sq mi) of the census block group
- `NumVeh` - number of vehicles owned or leased by the household
- `ZeroVeh` - dummy variable identifying whether the household has no vehicles
- `OneVeh` - dummy variable identifying whether the household has only one vehicle
- `Workers` - number of workers in the household
- `Age0to14` - number of persons in the 0 - 14 age group in the 
- `UrbanDev` - whether the block group is urban mixed-use
- `FwyLaneMiPC` - ratio of freeway lane miles to urbanized area population

Run for 1000 times for each household in the estimation data set

# Model 3: Simulated average DVMT

# Trace DVMT Calcs

https://github.com/visioneval/VisionEval/blob/master/sources/modules/VEHouseholdTravel/inst/module_docs/CalculateHouseholdDvmt.md